%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Scott Linderman's CV %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Layout, macros, and list environments live in cvstyle.sty. This file
%% is just the content.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt]{article}
\usepackage{cvstyle}

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\emergencystretch 3em

\nobibliography{cv}
\bibliographystyle{scottplain}

\makeheading{Scott W. Linderman}

\section{Contact Information}

% Address box
Wu Tsai Neurosciences Institute Room M252G\\
290 Jane Stanford Way\\
Stanford University\\
Stanford, CA 94305-4020\\
\\
% Non-snail-mail contact information
email:
%\texttt{{slinderman@seas.harvard.edu}}
\href{mailto:scott.linderman@stanford.edu}{\nolinkurl{scott.linderman@stanford.edu}}
\\
web:
\href{https://lindermanlab.github.io}{\nolinkurl{https://lindermanlab.github.io/}}

\section{Professional Experience}
\parbox[t]{\textwidth}{%
  \textbf{Stanford University}\\
  \cvline{Associate Professor, Department of Statistics}{2026-}\\
  \cvline{Assistant Professor, Department of Statistics}{2019-26}\\
  Faculty Scholar, Wu Tsai Neurosciences Institute\\
  Faculty Affiliate, Stanford Bio-X and Stanford AI Lab\\
  Co-Director, Stanford Center for Neural Data Science\\
}
\\
\parbox[t]{\textwidth}{%
  \cvline{\textbf{Engram}}{2025-}\\
  Co-Founder and Distinguished Scientist\\
  \href{www.engram.com}{\nolinkurl{www.engram.com}}\\
}
\\
\parbox[t]{\textwidth}{%
  \cvline{\textbf{Allen Institute}}{2025-}\\
  Affiliate, Studio for Data Driven Discovery\\
}
\\
\parbox[t]{\textwidth}{%
  \cvline{\textbf{Google}}{2022}\\
  Visiting Faculty Researcher, Google Brain\\
  Host: Kevin Murphy\\
}
\\
\parbox[t]{\textwidth}{%
  \cvline{\textbf{Columbia University}}{2016-19}\\
  Postdoctoral Fellow, Department of Statistics\\
  Advisors: Liam Paninski and David Blei\\
}
\\
\parbox[t]{\textwidth}{%
  \cvline{\textbf{Microsoft}}{2008-11}\\
  Software Development Engineer in Test\\
}

\section{Education}
\parbox[t]{\textwidth}{%
  \cvline{\textbf{Harvard University}}{2013-16}\\
  Ph.D., S.M., Computer Science\\
  Advisors: Ryan Adams and Leslie Valiant\\
}
\\
\parbox[t]{\textwidth}{%
  \cvline{\textbf{Cornell University}}{2004-08}\\
  B.S., Electrical and Computer Engineering\\
  \emph{Magna cum Laude} with Honors in Engineering\\
}

\section{Honors and Awards}
\begin{singlelist}
\setlength{\cvdatewidth}{0.45in}
\item \cvline{NSF CAREER Award}{2025}%
\item \cvline{McKnight Scholar Award}{2023}%
\item \cvline{Sloan Research Fellowship}{2022}%
\item \cvline{Allen Institute Next Generation Leaders Council}{2019}%
\item \cvline{Best Paper, Artificial Intelligence and Statistics (AISTATS)}{2017}%
\item \cvline{Leonard J. Savage Award, International Society for Bayesian Analysis}{2017}%
\item \cvline{Simons Collaboration on the Global Brain Postdoctoral Fellowship}{2016}%
\item \cvline{Siebel Scholarship}{2015}%
\item \cvline{National Defense Science and Engineering Graduate Fellowship}{2011}%
\end{singlelist}

\pagebreak

\section{Publications}

Note: all publications have authors listed in the order as published. Authorship convention in the field: lead senior author is listed last; lead junior author is listed first. (Asterisks denote joint lead or senior authorship).

\subsection{Books and Theses}
\begin{pubslist}
\item \textbf{Scott W. Linderman}. \textit{Machine Learning Methods for Neural Data Analysis}. 2024. \textit{In preparation. Available at} \url{https://slinderman.github.io/ml4nd}
\item \bibentry{linderman2016thesis}. \\
  \textbf{Received the Savage Award from the International Society for Bayesian Analysis}.
\end{pubslist}

\subsection{Preprints and Manuscripts Under Review}
\begin{pubslist}
\item \bibentry{smith2026closing}.
\item \bibentry{lee2026stiefel}. \textit{In revision at Neural Computation}.
\item \bibentry{levin2026crossbrain}. \textit{In submission to Nature Communications Biology}.
\item \bibentry{beller2025multimodal}. \textit{In submission to PNAS}.
\item \bibentry{xiao2025concerted}. \textit{Under review at Nature.}
\item \bibentry{versteeg2025computation}. \textit{Under review at PLoS CB.}
% \item \bibentry{levy2025natural}.
\item \bibentry{friedmann2024concerted}. \textit{In revision at Nature Neuroscience.}
\item \bibentry{kendrick2024transcriptomically}.
\end{pubslist}

\subsection{Peer reviewed journal, conference, and selected workshop papers}
\begin{pubslist}
\item \bibentry{nair2026representation}.
\item \bibentry{lotikar2026learning}.
\item \bibentry{gonzalez2026unifying}.
\item \bibentry{bedbrook2026lifelong}.
\item \bibentry{linderman2026bayesian}.
\item \bibentry{weinreb2026spontaneous}.
\item \bibentry{zhang2026decoding}.
\item \bibentry{he2026information}.
\item \bibentry{nair2025neural}.
\item \bibentry{gonzalez2025predictability}.
\item \bibentry{hu2025sing}.
\item \bibentry{zoltowski2025parallelizing}.
\item \bibentry{saadfalcon2025weaver}.
\item \bibentry{tanoh2025identifying}.
\item \bibentry{jiang2025extracting}. \\
  \textbf{Selected for Spotlight Presentation. (3.2\% of all submissions.)}
\item \bibentry{zhao2025informed}.
\item \bibentry{bukwich2025competitive}.
\item \bibentry{vloeberghs2025bayesian}.
\item \bibentry{narayan2025minions}.
\item \bibentry{linderman2025dynamax}.
\item \bibentry{willett2024brain}.
\item \bibentry{hu2024modeling}.
\item \bibentry{costacurta2024structured}.
\item \bibentry{gonzalez2024towards}.
\item \bibentry{mountoufaris2024neuropeptide}.
\item \bibentry{liu2024encoding}.
\item \bibentry{vinograd2024intrinsic}.
\item \bibentry{gershman2024explaining}.
\item \bibentry{weinreb2024keypoint}.
\item \bibentry{smekal2024theory}.\\
  \textbf{Selected for Spotlight Presentation.}
\item \bibentry{smith2023convolutional}.
\item \bibentry{hennig2023emergence}.
\item \bibentry{wang2023spatiotemporal}.
\item \bibentry{lawson2023nasx}.
\item \bibentry{lee2023switching}.
\item \bibentry{zhao2023revisiting}.
\item \bibentry{smith2023simplified}. \\
  \textbf{Selected for Oral Presentation. (1.5\% of all submissions).}
\item \bibentry{markowitz2023spontaneous}.
\item \bibentry{nair2023approximate}.
\item \bibentry{lawson2022sixo}. \\
    \textbf{Selected for Oral Presentation. (1.5\% of all submissions).}
\item \bibentry{costacurta2022distinguishing}.
\item \bibentry{beller2022looking}.
\item \bibentry{beron2022mice}.
\item \bibentry{lin2022imaging}.
\item \bibentry{linderman2022weighing}.
\item \bibentry{Williams2021single}.
\item \bibentry{smith2021reverse}.
\item \bibentry{williams2021generalized}.
\item \bibentry{yu2021fast}.
\item \bibentry{low2021dynamic}.
\item \bibentry{zhang2021gimbal}.
\item \bibentry{Mittal2020-gs}.
\item \bibentry{williams2020point}. \\
    \textbf{Selected for Oral Presentation (1.1\% of all submissions).}
\item \bibentry{glaser2020multi}.
\item \bibentry{tansey2020dose}.
\item \bibentry{zoltowski2020unifying}.
\item \bibentry{johnson2020probabilistic}.
\item \bibentry{sun2019voltage}.\\
  \textbf{Selected for Oral Presentation (0.5\% of all submissions).}
\item \bibentry{aposto2019mutually}.
\item \bibentry{schein2019poisson}.
\item \bibentry{batty2019behavenet}.
\item \bibentry{nassar2019treestructured}.
\item \bibentry{markowitz2018striatum}.
\item \bibentry{sharma2018pointprocess}.
\item \bibentry{mena2018learning}.
\item \bibentry{linderman2018reparameterizing}.
\item \bibentry{naesseth2018variational}.
\item \bibentry{linderman2017recurrent}.
\item \bibentry{naesseth2017rejection}.\\
  \textbf{Received Best Paper Award}.
\item \bibentry{linderman2017comment}.
\item \bibentry{linderman2017using}.
\item \bibentry{linderman2016bayesian}.
\item \bibentry{elibol2016crosscorpora}.
\item \bibentry{linderman2016nonparametric}.
\item \bibentry{linderman2015dependent}.
\item \bibentry{linderman2014framework}.
\item \bibentry{linderman2014discovering}.
\end{pubslist}

\subsection{Other preprints}
\begin{pubslist}
\item \bibentry{linderman2019hierarchical}.
\item \bibentry{linderman2015scalable}.
\end{pubslist}

% Advising
\section{Student\\Advising}

\subsection{Current Students}
\begin{singlelist}
\setlength{\cvdatewidth}{0.55in}

\item \cvline{Cole Citrenbaum, PhD Student, Stanford Statistics}{2025-}%

\item \cvline{Noah Cowan, PhD Student, Stanford Statistics}{2024-}%

\item \cvline{Yiqi Jiang, PhD Student, Stanford Electrical Engineering\newline\textit{Co-advised with Prof. Mark Schnitzer}}{2025-}%

\item \cvline{Etaash Katiyar, PhD Student, Stanford Statistics}{2024-}%

\item \cvline{Hannah Lee, PhD Student, Stanford Electrical Engineering}{2025-}%

\item \cvline{Hyun Dong Lee, PhD Student, Stanford Computer Science\newline\textit{Co-advised with Prof. Emily Fox}}{2022-}%

\item \cvline{Alisa Levin, PhD Student, Stanford Computer Science\newline\textit{Co-advised with Prof. Jaimie Henderson}}{2022-}%

\item \cvline{Jakub Sm\'{e}kal, PhD Student, Stanford Applied Physics}{2024-}%

\item \cvline{Henry Smith, PhD Student, Stanford Statistics\newline\textit{Co-advised with Prof. Brian Trippe}}{2024-}%

\item \cvline{Ian Christopher Tanoh, PhD Student, Stanford Statistics}{2022-}%

\item \cvline{Skyler Wu, PhD Student, Stanford Statistics}{2025-}%

\end{singlelist}

\subsection{Former Students}
\begin{singlelist}
\setlength{\cvdatewidth}{0.55in}

\item \cvline{Julia Costacurta, PhD Student, Stanford Electrical Engineering\newline\textit{Currently: Visiting Assistant Professor, Haverford College.}}{2021-25}%

\item \cvline{Xavier Gonzalez, PhD Student, Stanford Statistics\newline\textit{Currently: Technical Staff, Unconventional AI.}}{2022-26}%

\item \cvline{Amber Hu, PhD Student, Stanford Statistics\newline\textit{Currently: Research Scientist, Datadog.}}{2022-26}%

\item \cvline{Dieterich Lawson, PhD Student, Stanford Computer Science\newline\textit{Currently: Research Scientist, Google.}}{2020-23}%

\item \cvline{Matthew MacKay, PhD Student, Stanford Statistics\newline\textit{Currently: Technical Staff, Anthropic}}{2021-23}%

\item \cvline{Blue Sheffer, PhD Student, Stanford Computer Science\newline\textit{Currently: Founder, School of Song.}}{2019-21}%

\item \cvline{Jimmy Smith, PhD Student, Stanford ICME\newline\textit{Currently: Founding Scientist, Liquid AI}}{2019-24}%

\item \cvline{Libby Zhang, PhD Student, Stanford Electrical Engineering\newline\textit{Currently: Shanahan Postdoctoral Fellow, Allen Institute for Brain Science.}}{2019-25}%

\item \cvline{Yixiu Zhao, PhD Student, Stanford Applied Physics\newline\textit{Currently: Research Scientist, Basis Research Institute.}}{2020-25}%

\end{singlelist}

\section{Postdoctoral Advising}

\subsection{Current Postdocs}
\begin{singlelist}
\setlength{\cvdatewidth}{0.55in}

\item \cvline{Kanha Batra, Postdoctoral Researcher, Stanford Neurobiology\newline\textit{Co-advised with Prof. Lisa Giocomo}}{2025-}%

\item \cvline{E. Kelly Buchanan, Postdoctoral Researcher, Stanford Statistics\newline\textit{Co-advised with Prof. Chris R\'{e}.}}{2024-}%

\item \cvline{Aditi Jha, Postdoctoral Researcher, Stanford Statistics}{2024-}%

\item \cvline{Nicolas Zucchet, Postdoctoral Researcher, Stanford Statistics}{2026-}%

\end{singlelist}

\subsection{Former Postdocs}
\begin{singlelist}
\setlength{\cvdatewidth}{0.55in}

\item \cvline{Dan Biderman, Postdoctoral Resarcher, Stanford Statistics and CS\newline\textit{Co-advised with Prof. Chris R\'{e}.}\newline\textit{Currently: Co-Founder, Engram Lab.}}{2024-25}%

\item \cvline{Lea Duncker, Postdoctoral Researcher, Stanford Statistics and EE\newline\textit{Co-advised with Prof. Krishna Shenoy.}\newline\textit{Currently: Assistant Professor, Columbia University.}}{2021-23}%

\item \cvline{Elizabeth DuPre, Postdoctoral Researcher, Stanford Psychology\newline\textit{Co-advised with Prof. Russ Poldrack}\newline\textit{Currently: Postdoc, University of Montreal.}}{2022-24}%

\item \cvline{Aditya Nair, Postdoctoral Researcher, Stanford Statistics\newline\textit{Currently: Assistant Professor, LKCMedicine-NTU Singapore \& IMCB-A*STAR.}}{2024-25}%

\item \cvline{Andrew Warrington, Postdoctoral Researcher, Stanford Statistics\newline\textit{Currently: Research Scientist at GE Healthcare}}{2021-23}%

\item \cvline{Alex Williams, Postdoctoral Researcher, Stanford Statistics\newline\textit{Currently: Assistant Professor, NYU and Research Scientist, Flatiron Institute.}}{2019-21}%

\item \cvline{David Zoltowski, Postdoctoral Researcher, Stanford Statistics\newline\textit{Co-advised with Dr. David Sussillo}\newline\textit{Currently: Research Scientist, Google DeepMind.}}{2022-26}%

\end{singlelist}

\section{Research Support}

\subsection{Current Grants and Awards}
\begin{outerlist}

\item \grant[PI]{CAREER: State space models for neural and behavioral data}{NSF}{08/01/2025 - 07/31/2030}{Contact PI: S. Linderman}

\item \grant[MPI]{The brain as a control center for other organs during aging}{NIH}{12/01/2025 - 11/30/2030}{Contact PI: A. Brunet (Stanford)}

\item \grant[MPI]{Understanding sensorimotor control through realistic neuro-biomechanical simulation}{NIH}{04/01/2024 - 03/31/2027}{Contact PI: B. Olveczky (Harvard)}

\item \grant[MPI]{Unified, Scalable, and Reproducible Neurostatistical Software}{NIH}{07/01/23 - 06/30/2028}{Contact PI: A. Williams (NYU)}
% Total Amount: \$1,343,808

\item \grant[MPI]{Deconstructing the serotonin system in the mouse brain}{NIH}{04/01/23 - 03/31/2028}{Contact PI: L. Luo}
% Total Amount: \$3,953,554

\item \grant[Co-PI]{CRCNS: Deonstructing the time-varying dynamics of motor cortex in freely moving behavior}{NSF/NIH}{07/15/2022 - 04/30/2027}{Contact PI: P. Nuyujukian (Stanford)}
% Total Amount: \$2,000,893

\item \grant[Co-I]{The dynamics of neural representations for distinct spatial contexts and memory episodes}{NIH -- NIMH}{04/01/2022 - 03/31/2027}{Contact PI: L. Giocomo (Stanford)}
% Total award: \$1,981,193

\end{outerlist}

\subsection{Completed Grants and Awards}
\begin{outerlist}

\item \grant[PI]{Machine Learning Methods for Discovering Structure in Neural and Behavioral Data}{McKnight Foundation}{07/01/23 - 06/30/2026}{Contact PI: S. Linderman}
% Total Amount: \$225,000

\item \grant[Co-PI]{BRAID: DenPro3D Dendritic Processing of Spike Sequences in Biological and Artificial Brains}{NSF}{07/01/2022 - 06/30/2026}{Contact PI: K. Boahen (Stanford)}
% Total Amount: \$1,999,991

\item \grant[Co-I]{Probing the Dorsolateral Prefrontal Cortex and Central Executive Network for Improving Neuromodulation in Depression}{CRCNS US-France Research Proposal}{07/1/2021 - 06/30/2026}{Contact PI: C. Keller (Stanford)}
% Total award: \$1,226,978; Award number: R01MH129018

\item \grant[PI]{Discovering structure in neural and behavioral data}{Alfred P. Sloan Foundation}{09/15/2022 - 09/14/2024}{Contact PI: S. Linderman}
% Total Amount: \$75,000

\item \grant[MPI]{Toward a unified framework for dopamine signaling in the striatum}{NIH NINDS (Natl. Inst. of Neurological Disorders and Stroke)}{8/15/2019 - 7/31/2024}{Contact PI: B. Sabatini (Harvard)}
% Total award: \$18,505,241; Award number: 1U19NS113201

\item \grant[MPI]{Neural representation of mating partners by male C. elegans}{NIH NINDS (Natl. Inst. of Neurological Disorders and Stroke)}{8/15/2019 - 7/31/2024}{Contact PI: P. Sternberg (Caltech)}
% Total award: \$3,316,395; Award number: 1R01NS113119

\item \grant[Co-PI]{Dendritic Computation for Knowledge Systems}{Stanford Institute for Human-Centered Artificial Intelligence}{09/01/2022 - 08/31/2023}{Contact PI: K. Boahen (Stanford)}
% Total Amount: \$462,963

\item \grant[Co-PI]{Discovering repeating neural motifs representing sequenced behavior}{Simons Foundation (Simons Collaboration on the Global Brain)}{07/01/2020 - 06/30/2023}{Contact PI: B. Sabatini (Harvard)}
% Total award: \$36,000; Award number: 697092

\item \grant[Co-PI]{Multi-modal Inference in Brains, Minds, and Machines}{Stanford Institute for Human-Centered Artificial Intelligence}{3/13/2019 - 3/12/2020}{Lead PI: T. Gerstenberg (Stanford)}
% Total award: \$75,000

\item \grant[Co-PI]{Scalable probabilistic inference for mechanistic models: Bridging the gap between scientific modelling and machine learning}{Bavaria--California Technology Center (BaCaTeC)}{1/1/2019 - 6/1/2020}{Lead PI: J. Macke (Tubingen)}
% Total award: \euro{}6,000

\end{outerlist}

\section{Teaching Experience}
\begin{singlelist}
\item \cvline{STATS305B: Applied Statistics II}{2024-25}%
\item \cvline{STATS305C: Applied Statistics III}{2022,23,26}%
\item \cvline{STATS320: ML Methods for Neural Data Analysis}{2021,23,25}%
\item \cvline{STATS271/371: Applied Bayesian Statistics}{2021}%
\item \cvline{STATS215: Statistical Models in Biology}{2020}%
\end{singlelist}

% Service
\section{Professional Service}

\subsection{Summer School Organization and Teaching}
\begin{singlelist}
\setlength{\cvdatewidth}{0.55in}
\item \cvline{Allen Institute Summer Workshop on the Dynamic Brain.}{2021-}%
\item \cvline{Woods Hole Methods in Computational Neuroscience Course.}{2024-}%
\item \cvline{Neuromatch Academy, Executive Committee (Co-Chair of Projects).}{2022-23}%
\item \cvline{JAX Short Course on Machine Learning for Quantifying Behavior.}{2022-24}%
\end{singlelist}

\subsection{Conference and Workshop Organization}
\begin{singlelist}
\setlength{\cvdatewidth}{0.75in}
\item \cvline{Co-Organizer, Statistical Analysis of Neural Data (SAND)}{2025}%
\item \cvline{Program Committee, Bernstein Conference}{2024-25}%
\item \cvline{Program Committee, COSYNE Conference}{2022-24}%
\item \cvline{Co-Organizer, COSYNE Workshop}{2014,17,25}%
\item \cvline{Co-Organizer, ICML Workshop}{2020}%
\item \cvline{Co-Organizer, NeurIPS Workshop}{2019}%
\end{singlelist}

\subsection{Conference Area Chair}
\begin{singlelist}
\setlength{\cvdatewidth}{0.55in}
\item \cvline{Neural Information Processing Systems (NeurIPS)}{2019-}%
\item \cvline{International Conference on Learning Representations (ICLR)}{2021-23}%
\item \cvline{International Conference on Machine Learning (ICML)}{2021-23}%
\item \cvline{Conference on Artificial Intelligence and Statistics (AISTATS)}{2021-23}%
\end{singlelist}

\subsection{Journal and Conference Reviewing}
\begin{singlelist}
\item Annals of Applied Statistics
\item Biometrika
\item AAAI Conference on Artificial Intelligence (AAAI)
\item eLife
\item IEEE Transactions on Signal Processing
\item International Conference on Machine Learning (ICML)
\item International Conference on Artificial Intelligence and Statistics (AISTATS)
\item Journal of the American Statistical Association (JASA)
\item Journal of Computational Neuroscience
\item Nature
\item Nature Methods
\item Nature Communications
\item Neural Computation
\item Neural Information Processing Systems (NeurIPS)
\item PLoS Computational Biology
\item SIAM Journal on Applied Dynamical Systems (SIADS)
\end{singlelist}

% Talks
\section{Selected Talks}

\begin{singlelist}
\setlength{\cvdatewidth}{0.9in}
\item \cvline{Neuroscience Theory Center, Columbia University}{01/23/2026}%
\item \cvline{Redwood Center for Theoretical Neuroscience, UC Berkeley}{11/12/2025}%
\item \cvline{Wharton Statistics Seminar, University of Pennsylvania}{10/15/2025}%
\item \cvline{Statistics Department, Duke University}{09/19/2025}%
\item \cvline{Neurobiology Department, Duke University}{09/16/2025}%
\item \cvline{Princeton Neuroscience Institute, Princeton University}{10/24/2024}%
\item \cvline{Jackson Laboratory}{10/18/2024}%
\item \cvline{Kempner Institute, Harvard University}{10/11/2024}%
\item \cvline{Chen Institute for Neuroscience Director's Seminar, Caltech}{06/04/2024}%
\item \cvline{University of Washington CoNectome Annual Symposium}{05/13/2024}%
\item \cvline{Two Sigma Investments}{05/08/2024}%
\item \cvline{Simons Collaboration on the Global Brain Annual Meeting}{05/06/2024}%
\item \cvline{International Winter Neuroscience Conference}{04/09/2024}%
\item \cvline{COSYNE Workshop on Reconstructing Dynamical Systems from Neural Data}{03/04/2024}%
\item \cvline{Statistics Seminar, Harvard University}{11/27/2023}%
\item \cvline{Neuroscience Seminar, Cold Spring Harbor Laboratory}{11/20/2023}%
\item \cvline{Biostatistics Seminar, University of North Carolina, Chapel Hill}{09/07/2023}%
\item \cvline{IDEAS Seminar Series in Theoretical Neuroscience, Georgia Tech}{03/28/2023}%
\item \cvline{COSYNE Workshop on Generative Models for Neural/Behavioral Data Analysis}{03/14/2023}%
\item \cvline{Machine Learning Seminar, Memorial Sloan-Kettering}{12/06/2022}%
\item \cvline{NeuroTheory Seminar, Columbia University}{12/05/2022}%
%\item \cvline{Gaze Meets ML Workshop, NeurIPS}{12/03/2022}%
\item \cvline{Neuroscience Seminar, UCSD}{09/27/2022}%
\item \cvline{Neuroscience Seminar, University of Chicago}{10/25/2022}%
%\item \cvline{Short Course on Machine Learning Methods for Quantifying Behavior, JAX Laboratories}{10/12/2022}%
\item \cvline{Joint Statistics Meeting (JSM), Contributed Talk}{08/01/2022}%
\item \cvline{International Society for Bayesian Analysis, Contributed Talk}{07/01/2022}%
\item \cvline{Stanford-Berkeley Joint Statistics Colloquium, UC Berkeley}{04/19/2022}%
\item \cvline{Statistics Seminar, University of Connecticut}{04/13/2022}%
\item \cvline{External Seminar Series, Gatsby Unit, UCL}{01/12/2022}%
\item \cvline{Neuroscience Seminar, Boston University}{11/03/2021}%
\item \cvline{SymPOSEium, University of Minnesota}{10/14/2021}%
\item \cvline{CRCNS Workshop on Large Scale Neuroscience, NYU}{10/09/2021}%
\item \cvline{Bernstein Conference on Theoretical Neuroscience, Berlin}{09/22/2021}%
\item \cvline{Biostatistics Seminar, University of California, Berkeley}{04/12/2021}%
\item \cvline{Statistics Seminar, University of California, Los Angeles}{03/04/2021}%
\item \cvline{Statistics Seminar, University of British Columbia}{11/03/2020}%
\item \cvline{Biostatistics Seminar, Duke University}{10/23/2020}%
%\item \cvline{Online Workshop on Linking Behavior and Neural Dynamics, LMU M\"{u}nchen}{10/16/2020}%
\item \cvline{MBCT Seminar, Stanford University}{10/12/2020}%
%\item \cvline{Bernstein Workshop on Inferring and Testing Optimality in Perception and Neurons}{09/29/2020}%
%\item \cvline{SIAM Minisymposium on Machine Learning and Control Theory for Whole Brain Activity}{06/26/2020}%
\item \cvline{ML Tea, Gatsby Computational Unit, University College London}{04/24/2020}%
\item \cvline{Statistics Seminar, University of California, Davis}{04/23/2020}%
\item \cvline{COSYNE Workshop on Interpretable Computational Neuroscience}{03/01/2020}%
%\item \cvline{Information Systems Laboratory (ISL) Colloquium, Stanford University}{02/13/2020}%
\item \cvline{Chan Zuckerberg Institute}{01/31/2020}%
\item \cvline{Google Brain}{01/22/2020}%
\item \cvline{Institute of Neuroscience Seminar.  University of Oregon}{11/21/2019}%
\item \cvline{Allen Institute for Brain Science. Seattle, WA}{11/12/2019}%
\item \cvline{Biostatistics Workshop.  Stanford University}{10/24/2019}%
%\item \cvline{Society for Neuroscience Virtual Conference on Machine Learning in Neuroscience}{06/26/2019}%
%\item \cvline{Harvard University}{04/12/2019}%
\item \cvline{COSYNE Workshop on Social Behavior. Lisbon, Portugal}{03/05/2019}%
\item \cvline{COSYNE Workshop on Data, dynamics, and computation: Using data driven methods to ground mechanistic theory.}{03/04/2019}%
%\item \cvline{Theoretical and Computational Neuroscience Annual Conference, Gulf Coast Consortium}{02/01/2019}%
\item \cvline{NeuroNex Workshop, Rice and Baylor University}{01/31/2019}%
\item \cvline{Applied Math Seminar, Yale University}{01/29/2019}%
\item \cvline{Artificial Intelligence Seminar, Cornell University}{09/28/2018}%
\item \cvline{Center for Neuroengineering and Computation Seminar, Columbia University}{09/24/2018}%
\item \cvline{Simons Collaboration on the Global Brain Postdoc Meeting}{09/20/2018}%
\item \cvline{Air Force Research Laboratory, Rome, NY}{08/27/2018}%
\item \cvline{IACS Seminar, Stony Brook University}{07/13/2018}%
%\item \cvline{Simons Workshop on Manifold Discovery}{04/06/2018}%
\item \cvline{Statistics Department, Stanford University}{04/05/2018}%
\item \cvline{Allen Institute for Brain Science}{03/28/2018}%
\item \cvline{Paul Allen School of Computer Science and Engineering, University of Washington}{03/26/2018}%
\item \cvline{Janelia Farm Research Campus}{02/28/2018}%
\item \cvline{Stanford Neurosciences Institute, Stanford University}{02/20/2018}%
\item \cvline{Zuckerman Institute, Columbia University}{02/13/2018}%
\item \cvline{Statistics Department, Columbia University}{02/12/2018}%
\item \cvline{Biophysics Department, University of Washington}{02/05/2018}%
\item \cvline{Center for Brain Science, Harvard University}{01/30/2018}%
%\item \cvline{Project SEM Multidisciplinary University Research Initiative (MURI), Princeton University}{09/17/2017}%
%\item \cvline{Air Force Research Laboratory, Rome, NY}{08/07/2017}%
%\item \cvline{Princeton Neurosciences Institute, Princeton University}{06/22/2017}%
%\item \cvline{Machine Learning and Friends Seminar, UMass Amherst}{05/04/2017}%
%\item \cvline{Models, Inference, and Algorithms (MIA) Seminar, The Broad Institute}{04/12/2017}%
%\item \cvline{Workshop on High-Dimensional Neuro-Behavioral Analysis, COSYNE}{02/28/2017}%
%\item \cvline{Statistical Analysis of Neural Data Seminar, Stanford University}{02/22/2017}%
%\item \cvline{Connectomics II Workshop, Neural Information Processing Systems (NIPS)}{12/10/2016}%
%\item \cvline{Statistics and Math Reading Club, The Broad Institute}{10/19/2015}%
%\item \cvline{Computational Statistics and Neuroscience Seminar, Columbia University}{03/18/2015}%
%\item \cvline{Machine Learning and Friends, University of Massachusetts at Amherst}{02/12/2015}%
%\item \cvline{Applied Statistics Seminar, University of Washington}{01/08/2015}%
%\item \cvline{Harvard Center for Brain Science (CBS) Neurolunch}{12/03/2014}%
% \item \cvline{Lazer Lab Meeting, Northeastern University}{09/04/2014}%
%\item \cvline{Harvard Computer Science Colloquium}{07/24/2014}%
% \item \cvline{David Cox Lab Meeting, Harvard University}{07/10/2014}%
% \item \cvline{Adam Cohen Lab Meeting, Harvard University}{05/05/2014}%
%\item \cvline{Boston Data Mining Meetup}{05/01/2014}%
% \item \cvline{Applied Statistics Workshop, Harvard University}{09/04/2013}%
\end{singlelist}

\end{document}